\setlength{\columnsep}{3pt}
\begin{flushleft}
	\bigskip
	\paragraph{What is a link?}
	\begin{itemize}
		\item A link allows two or more names for the same file/directory.
		\item There are two types of links:
		\begin{itemize}
			\item \textbf{Hard link}:
			\begin{itemize}
				\item Can be created only for file and points to the file's inode number.
				\item Cannot be created across filesystem.
				\item Inode for all the hard links are same .
			\end{itemize}
			
			\bigskip
			\begin{tcolorbox}[breakable,notitle,boxrule=-0pt,colback=pink,colframe=pink]
				\color{black}
				\fontdimen2\font=9pt
				Syntax: ln source\_filename  hard\_link\_name
				\fontdimen2\font=4pt
			\end{tcolorbox}
			Eg:
			\bigskip
			\begin{tcolorbox}[breakable,notitle,boxrule=-0pt,colback=black,colframe=black]
				\fontdimen2\font=9pt
				\color{yellow}
				\# Create hard link for abc.txt file:
				\newline
				\color{green}
				\# ln abc.txt /tmp/new\_link.txt
				\newline
				\newline
				\color{yellow}
				\# Check the inode of abc.txt \& /tmp/new\_link.txt 
				\newline
				\color{green}
				\# ls -i abc.txt  /tmp/new\_link.txt
				\newline
				\color{white}
				3052945 abc.txt
				\newline
				3052945 /tmp/new\_link.txt
				\fontdimen2\font=4pt
			\end{tcolorbox}
			\bigskip
			\begin{tcolorbox}[breakable,notitle,boxrule=1pt,colback=yellow,colframe=yellow]
				\color{black}
				Note: Notice how the inode number for hard link are same.
			\end{tcolorbox}
			
			
			\newpage
			\item \textbf{Soft link}:
			\begin{itemize}
				\item Can be created for file as well as directory.
				\item Can be created across filesystems.
				\item Inode for soft link are different.
			\end{itemize}
			\bigskip
			\begin{tcolorbox}[breakable,notitle,boxrule=-0pt,colback=pink,colframe=pink]
				\color{black}
				\fontdimen2\font=9pt
				Syntax: ln -s source\_file\_or\_directory  softlink\_name
				\fontdimen2\font=4pt
			\end{tcolorbox}
			Eg:
			\begin{tcolorbox}[breakable,notitle,boxrule=-0pt,colback=black,colframe=black]
				
				\fontdimen2\font=9pt
				\color{yellow}
				\# Create soft link for /tmp folder:
				\newline
				\color{green}
				\$ ln -s /tmp /home/sample/
				\newline
				\newline
				\color{yellow}
				\# Check the inode of /tmp \&  /home/sample
				\newline
				\color{green}
				\$ ls -i /tmp  /home/sample
				\newline
				\color{white}
				3052047 /tmp
				\newline
				2052047 /home/sample
				\fontdimen2\font=4pt
			\end{tcolorbox}

			\bigskip
			\begin{tcolorbox}[breakable,notitle,boxrule=1pt,colback=yellow,colframe=yellow]
				\color{black}
				Note: Notice how the inode number for soft link are different.
			\end{tcolorbox}


		\end{itemize}
		
	\end{itemize}
	, 
	

	
\end{flushleft}

\newpage

